Loop

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

 this stupid figure has to get embedded    
 ![Fig1](./executableMS/Figures/Figure 1.png)

@@

![Fig2](./executableMS/Figures/Figure 2.png)

>>>>

 this stupid figure has to get embedded    
 Fig (/Figures/Figure 1.png)

```{r Fig1, echo = FALSE, fig.width = 4, fig.height = 8, fig.cap=Figure 1]"}
include_graphics(here("Figures", "Figure 1.png"))
```

@@

 (/Figures/Figure 2.png)
 ```{r Fig2, echo = FALSE, fig.width = 4, fig.height = 4, fig.cap=Figure 2]"}
include_graphics(here("Figures", "Figure 2.png"))
```
